Supermassive black holes and their host spheroids \\ I. Galaxy vivisection

### 2015-10-01 papers/data_paper/datapaper.tex
submission day
holidays

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}

@@

\shorttitle{True-to-life galaxy decomposition}
\shortauthors{Savorgnan \& Graham}

@@

\title{Supermassive black hole and host spheroid affairs \\ I. True to life, physically motivated galaxy decomposition}

@@

the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction}; Fontanot et al. \emph{submitted}) 

@@

Most of the morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII-MNRAS}.

@@

a strong $M_{\rm BH}-n_{\rm sph}$ correlation was recovered. 
The fact that none of the four studies obtained a significant $M_{\rm BH}-n_{\rm sph}$ correlation with their individual measurements 
is indicative of non accurate galaxy decompositions. }.

@@

as opposed to \cite{beifiori2012} who claimed that the spheroid mass is a better tracer of $M_{\rm BH}$ than the galaxy mass.

@@

which is an excellent proxy for the stellar mass, superior to the $K$-band (\citealt{sheth2010} and references therein).

@@

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs). 
%listed in Table \ref{tab:obs}.
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be %``enhanced Level 1 products'', or
corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It appears as a decaying trail of pixels, repeating every fourth column.
``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

\subsubsection{Mosaicking}
We performed image mosaicking using the MOPEX package \citep{makovozmarleau2005mopex}.
This enabled the production of suitably wide-field-of-view images for accurate sky background subtraction.
Individual cBCD frames with exposure time of $1~\rm sec$ were rejected.
Permanent or semi-permanent bad pixels, contained in a semi-static mask (the ``pmask''), were ignored.
Each AOR is associated to a specific pmask. 
Therefore, when multiple AORs were available for the same galaxy, 
we merged the different pmasks. 
Cosmic ray rejection was performed with the dual outlier and multi-frame techniques.
The pixel size of the mosaic was set to be the same as the input cBCD frames ($1''.22 \times 1''.22$).
For $3.6~\rm \mu m$ observations with this pixel scale, 
the photometric zeropoint magnitude is $m_{\rm zp} = 17.26 \rm~mag$.
The orientation of the mosaic was set to the average rotation angle of the input cBCD frames. 
%{\bf TBD: not n-e oriented or re-sampled because problems with 2d PSF. }
Individual cBCD frames were combined together into a single mosaic with the default linear interpolation algorithm.

\subsubsection{Overlap correction}
Before generating a mosaic, MOPEX can perform background matching among the individual frames
by using the \emph{overlap} module. 
This module calculates and applies an additive correction to the individual frames,
producing a consistent background across the mosaicked image.
According to the \emph{Spitzer Data Cookbook}, the use of the \emph{overlap} module is not particularly recommended for 
$3.6~\rm \mu m$ observations. 
However, after a visual inspection of the mosaics obtained without activating the \emph{overlap} module,
we found that all the mosaics obtained from multiple AORs were affected by patchiness, 
due to bias fluctuations in the CCD array.
For this reason, we re-generated the multiple-AORs mosaics by activating the \emph{overlap} correction,
which successfully removed the ``chessboard'' pattern (see Figure \ref{fig:overlap} for an example).

@@

\subsubsection{1D PSF}
A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
%We employed both a Gaussian and a Moffat \citep{moffat1969} profile. 
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained %$FWHM = 2''.03$ for the Gaussian function,
$(\alpha, \beta) = (2''.38, 4.39)$.

\subsubsection{2D PSF}
The IRAC support team provides users with a two-dimensional instrument Point Response Function (PRF) at $3.6~\rm \mu m$.
However, while this helped remove the extended wings of saturated stars (see Section \ref{sec:aesth}), 
we found this PRF to be inadequate for the purposes of our modelling.
In fact, the $FWHM$ of the IRAC instrument PRF ($\sim 1''.8$), as measured by the IRAF task {\tt imexamine}, 
is systematically smaller than the average $FWHM$ of ``real'' stars ($\sim 2''.0$). 
Figure \ref{fig:psf} illustrates this issue.
We also tested the IRAC PRF by providing it as the input Point Spread Function (PSF) for Galfit 
and fitting a number of stars in different image mosaics.
A visual inspection of the fit residuals confirmed that the IRAC instrument PRF is narrower than ``real'' point sources.
For this reason, we constructed our 2D PSF according to the following method 
(as directed by C. Peng, private communication).\\
We provided the IRAC instrument PRF as the input PSF for Galfit 
and simultaneously fit 7 bright stars (belonging to different mosaics), 
modeling the stars with Moffat profiles 
and constraining all the profiles to have the same $(\alpha, \beta)$, position angle and axis ratio.
The 2D PSF image was then obtained by taking the best fit Moffat model -- the same best-fit model for all 7 stars, by construction -- 
and convolving it with the IRAC instrument PRF.
The advantage of this method is to obtain a 2D PSF that is wider than the instrument PRF, 
but maintains the asymmetric features of the instrument PRF (e.g.~wings and spikes).
%This procedure was repeated using a Moffat profile in place of the Gaussian profile.
We then tested this 2D PSF 
on a number of stars (these stars were different from the 7 stars employed to build the 2D PSF image)
and verified that it correctly reproduces the shape of ``real'' point sources.

@@

\subsection{Additional data}
\label{sec:adddata}
\subsubsection{Kinematics}
\label{sec:kinem}
A kinematical classification (slow/fast rotator) is available for 34 of our 75 galaxies 
from the ATLAS$^{\rm 3D}$ survey \citep{atlas3dIII-MNRAS} 
and for 3 additional galaxies from \citet{scott2014}.
This classification (Table \ref{tab:sample}, column 7) 
concerns the kinematic properties of galaxies within the spectroscopic instrument's field-of-view, 
but does not contain additional information -- crucial for our analysis -- about kinematic substructures, 
such as embedded disks or kinematically decoupled components, 
which can require separate modeling.
For this reason, we also visually inspected the velocity fields of our galaxies, 
when available from the literature.
Velocity maps were taken from the ATLAS$^{\rm 3D}$ survey for 34 galaxies 
(observed with SAURON by \citealt{krajnovic2011}),
from \citet{scott2014} for 2 galaxies 
(observed with WiFeS)
and from the SLUGGS survey for 12 galaxies 
(observed with DEIMOS by \citealt{arnold2014}).
While the field-of-views of SAURON ($33'' \times 41''$) and WiFeS ($25'' \times 38''$) 
reach to about one galaxy effective radius (for our local galaxies),
observations taken with DEIMOS can probe the galaxy kinematics well beyond two effective radii.

@@

\section{Analysis}
\label{sec:anal}
\subsection{Isophotal analysis}
We performed an isophotal analysis of our galaxies using the IRAF task {\tt ellipse} \citep{taskellipse}, 
which fits elliptical isophotes to galaxy images.
The center of the isophotes was held fixed, while the ellipticity ($\epsilon$), the position angle ($P.A.$),  
and the amplitude of the fourth harmonic\footnote{The amplitude of the fourth harmonic deviations from perfect ellipses 
($B4$) parameterizes the diskyness ($B4>0$) or boxyness ($B4<0$) of the isophotes.} ($B4$) were allowed to vary with radius.
The step in semi-major axis length between successive ellipses was first set to increase linearly, 
and then geometrically in our second run\footnote{In the case of linear steps, 
the semi-major axis length for the next ellipse was calculated by adding $1$ pixel to the current length.
In the case of geometric steps, the semi-major axis length for the next ellipse 
was calculated as $1.1$ times the current length.}.
As a result, for each galaxy we produced respectively a ``linearly sampled'' and a ``logarithmically sampled'' 
surface brightness profile along the major-axis. 
Major-axis surface brightness profiles were additionally converted into the equivalent-axis,
i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
equivalent to the circularized radius.
This resulted in 4 profiles per galaxy.
Isophotes corresponding to an intensity less than 
three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$) were ignored.
Some surface brightness profiles were truncated at our discretion before the $3 \times RMS_{\rm sky}$ limit, 
according to specific technical reasons (e.g.~contamination from light of a neighboring galaxy, 
disturbed morphology in the galaxy outskirts, etc.).
Individual cases are discussed in Section \ref{sec:indgal}.

@@

\subsection{1D fitting routine}
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile, 
although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
The all too often over-looked flaw with (signal-to-noise)-based weighting schemes 
is that they immediately become an incorrectly biased weighting schemes when additional components are present but not modelled.
For example, fitting a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
a (signal-to-noise)-based weighting scheme 
and results in S\'ersic parameters which describe the spheroid less accurately than had no (signal-to-noise)-weighting been used.
While we have paid careful attention to the components in each galaxy, 
this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
What is best in theory is not always best in practice -- in this case, because theory does not allow for unknown additional components
that are modelled.

@@

that fades toward larger radii. \\
%As an illustration, we consider the galaxy NGC 3377.
%For this galaxy, \citet{arnold2014} reported a strong decline in local specific angular momentum beyond $\sim 35''$, 
%with a disk-to-bulge transition occurring at about $\sim 50''$.
%They did attempt a three-component decomposition (accounting for a bulge, an embedded disk and a central cusp), 
%but unfortunately they fit the spheroidal component with a limited two-parameter $R^{1/4}$ profile {\bf TBD: cite de vaucouleurs} 
%rather than a three-parameter $R^{1/n}$ S\'ersic function.
%Here we used a surface brightness profile twice as extended as that used by \citet{arnold2014} 
%and we identified a nuclear disk and an intermediate-scale disk, both embedded in a larger spheroidal component (see Figure \ref{fig:n3377ex}).
%The presence of an intermediate-scale disk is evident from the unsharp mask of the image mosaic 
%and also from the ellipticity profile, which increases with increasing radius until $R \sim 45''$ (along the major-axis) 
%and dramatically drops at larger radii.
%The nuclear disk can be spotted from the peak at $R \sim 5''$ in the $B4$ profile.
%In our galaxy model for NGC 3377, 
%the difference between the S\'ersic profile of the bulge and the exponential profile of the intermediate-scale disk is minimum in correspondence 
%of the maximum ellipticity, 
%thus our model correctly reproduces the isophotal properties of the galaxy. 
%The residuals of the fit, especially along the major-axis, display some minor structures which indicate that 
%the bulge S\'ersic index might have been slightly overestimated.
%This could be due to the fact that the embedded disk would be better described by a truncated exponential function.
%Alternatively, a contribution from a stellar halo (not included in our model) at large radii could be the reason of a 
%too large S\'ersic index for the bulge. 
%Our equivalent-axis decomposition results in a bulge component that accounts for 94\% of the total luminosity, 
%an intermediate-scale embedded disk contributing to 5\% 
%and a nuclear disk with 1\% of the total light. \\
%A similar situation occurs for the galaxy M59 (see Figure \ref{fig:m59ex}), 
%for which our equivalent-axis model returns a spheroidal component and an embedded disk 
%contributing to 92\% and 8\% of the total light respectively. \\
%The edge-on embedded disk of the S\'ersic galaxy NGC 1332 (see Figure \ref{fig:n1332ex}) was hard to model with an exponential function, 
%leading us to prefer a low-$n$ S\'ersic profile. 
%Our equivalent-axis decomposition returns a spheroidal component accounting for 95\% of the total light,
%and an embedded disk accounting for the remaining 5\%.
%In passing, we note that the bulge-disk decomposition performed by \citet{rusli2011} on NGC 1332 
%is significantly different from our best-fit model.
%\citet{rusli2011} did not identify an intermediate-scale embedded disk, 
%but instead proposed a model featuring a S\'ersic bulge ($n \sim 2.3$, $R_{\rm e} \sim 8''$), accounting for 43\% of the total light, 
%and a large-scale exponential disk. 
%This result led them to the conclusion that NGC 1332 is a disk dominated lenticular galaxy 
%and is displaced from the $M_{\rm BH} - L_{\rm K,sph}$ (black hole mass vs. $K$-band spheroid luminosity) relation of \citet{marconihunt2003} 
%by an order of magnitude along the $M_{\rm BH}$ direction.
%Assuming instead that, as suggested by our model, 
%the galaxy spheroid is a factor of two more luminous than what claimed by \citet{rusli2011}, 
%NGC 1332 would no longer be an outlier in the $M_{\rm BH} - L_{\rm K,sph}$ diagram (see Figure \ref{fig:n1332pl}), 
%perfectly fitting within the $1\sigma$ scatter of the $M_{\rm BH} - L_{\rm K,sph}$ relation for S\'ersic bulges of \citet{grahamscott2013}. \\

@@

As noted, we were able to successfully fit bars with a Ferrer function or a low-$n$ S\'ersic model ($n \sim 0.2$). \\

@@

whereas resolved nuclear components were modeled with (PSF-convolved) narrow Gaussian functions. \\

@@

%\cite{sani2011} modeled this galaxy with a S\'ersic-bulge + Gaussian-AGN 
%($R_{\rm e} = 27''.2$, $n = 3.0$). 

@@

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n3377_1Dfit.eps}
%\caption{the galaxy NGC 3377. 
%The left panels refer to the major-axis $R_{\rm maj}$, 
%whereas the right panels refer to the equivalent-axis $R_{\rm eq}$.
%The top panels display the galaxy surface brightness radial profiles obtained with a linear sampling. 
%The black points are the observed data.  
%The color lines represent the individual (PSF-convolved) model components:
%red=S\'ersic (bulge), blue=exponential (disk). 
%The best-fit parameters for the S\'ersic profile are included.
%The total (PSF-convolved) model is shown with a black dashed line, 
%but it is hard to distinguish because it almost perfectly matches the data.
%The horizontal grey dashed line indicates the $3~RMS_{\rm sky}$ level.
%$\Delta$ denotes the rms scatter of the fit in units of $\rm mag~arcsec^{-2}$.
%$\Delta \mu$ are the residuals from the fit.
%The six panels below show the ellipticity ($\epsilon$), position angle ($PA$) and $B4$ radial profiles.
%}
%\label{fig:n3377ex}
%\end{center}
%\end{figure*}

@@

%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/m59_1Dfit.eps}
%\caption{the galaxy M59. 
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:m59ex}
%\end{center}
%\end{figure*}
%
%\begin{figure*}[h]
%\begin{center}
%\includegraphics[width=\fitfigurewidth]{images/n1332_1Dfit.eps}
%\caption{the galaxy NGC 1332.
%The figure caption is the same as Figure \ref{fig:n3377ex}. 
%Empty data points represent data excluded from the fit.}
%\label{fig:n1332ex}
%\end{center}
%\end{figure*}
%
%\begin{figure}[h]
%\begin{center}
%\includegraphics[width=\columnwidth]{images/mbhmagk_n1332.pdf}
%\caption{The location of the S\'ersic galaxy NGC 1332 in the black hole mass versus $K$-band spheroid absolute magnitude diagram,
%according to our galaxy decomposition. 
%The red and blue solid lines show the scaling relations for core-S\'ersic and S\'ersic galaxies, respectively, 
%reported by \citet{grahamscott2013}, 
%while the shaded areas mark the $1\sigma$ errors.}
%\label{fig:n1332pl}
%\end{center}
%\end{figure}

\subsection{2D fits}
\label{sec:2d}
Two-dimensional decompositions were carried out using the software \textsc{Imfit} \citep{imfit}.
For each galaxy, we built a 2D model that was consistent with the corresponding 1D model in terms of number and type of components. 
Because the Ferrer profile is not made available in \textsc{Imfit},
bars were fit with a 2D Gaussian function. \\
The 2D decomposition of NGC 2974 is presented in Figure \ref{fig:n29742d}. 
The galaxy was modeled with a S\'ersic bulge, an exponential disk and a Gaussian bar.
The nuclear component was masked and the ring was not 
modeled\footnote{We built the 2D model first including and then omitting a gaussian ring component, 
but both models converged to the same solution, i.e.~the fit ``ignored'' the presence of the faint ring. 
This did not happen in the 1D decomposition because of the different weighting scheme used by the fitting routines.}. 
Our best-fit 2D model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 10.5~\rm arcsec$, 
a bulge S\'ersic index $n_{\rm sph} = 1.3$ and a $3.6~\rm \mu m$ bulge apparent magnitude $m_{\rm sph} = 8.39~\rm mag$, 
in fairly good agreement with our 1D decomposition. 
Fits and descriptions for the other galaxies are available online.

>>>>

\usepackage{natbib}
\bibliographystyle{apj}
\usepackage{longtable}
\usepackage[]{graphicx}
\usepackage{amsmath}
\usepackage{natbib}
\usepackage{tabularx}
\usepackage{bm}
\usepackage{hyperref}

@@

\shorttitle{Galaxy vivisection}
\shortauthors{Savorgnan \& Graham}

@@

\title{Supermassive black holes and their host spheroids \\ I. Galaxy vivisection}

@@

the local black hole mass function (e.g.~\citealt{salucci1999,graham2007smbhmassfunction,shankar2009,shankar2013,fontanot2015}) 

@@

Most of the morphologically classified elliptical galaxies in the ATLAS$^{\rm 3D}$ sample are fast rotators \citep{atlas3dIII}.

@@

a strong $M_{\rm BH}-n_{\rm sph}$ correlation was recovered. }.

@@

as opposed to \cite{beifiori2012} who claimed that the spheroid mass is a better tracer of $M_{\rm BH}$ than the galaxy mass 
{\bf (see also \citealt{kormendygebhardt2001,erwingadotti2012})}.

@@

which is an excellent proxy for the stellar mass, superior to the $K$-band \citep{junim2008,sheth2010}.

@@

\subsection{\emph{Spitzer}/IRAC observations}
\subsubsection{Data acquisition}
For each of our 75 galaxies, we downloaded from the 
Spitzer Heritage Archive\footnote{\url{http://irsa.ipac.caltech.edu/applications/Spitzer/SHA/}} 
all the available $3.6~\rm \mu m$ IRAC Astronomical Observation Requests (AORs). 
Each AOR is an individual Spitzer observation sequence, and
includes a number of data frames (the individual exposures) and the calibration data.
The data frames were selected to be %``enhanced Level 1 products'', or
corrected Basic Calibrated Data (cBCD), produced by the IRAC Level 1 pipeline. 
This automatic pipeline takes a single ``raw'' image, removes the scattered light, 
and performs dark subtraction, flatfielding correction and flux calibration (into units of $\rm MJy~sr^{-1}$). 
The final product (the BCD) is a flux-calibrated image which has had all the well-understood instrumental signatures removed.
BCD frames are further processed through an ``artifact correction'' pipeline 
that mitigates the commonly found artifacts of stray light, saturation, ``muxbleed'' and column pulldown\footnote{Stray light 
includes scattered light from stars outside the array location as well as filter ghosts from bright stars. 
Multiplexer bleed, or ``muxbleed'', can be generated by stars, hot pixels, and particle hits.
It appears as a decaying trail of pixels, repeating every fourth column.
``Column pulldown'' is caused by a bright pixel that triggers a bias shift within its respective column, 
creating a lower background value throughout the entire column than in the surrounding columns.}.
After the artifact correction has been applied, the BCD becomes a cBCD.

\subsubsection{Mosaicking}
We performed image mosaicking using the MOPEX package \citep{makovozmarleau2005mopex}.
This enabled the production of suitably wide-field-of-view images for accurate sky background subtraction.
Individual cBCD frames with exposure time of $1~\rm sec$ were rejected.
Permanent or semi-permanent bad pixels, contained in a semi-static mask (the ``pmask''), were ignored.
Each AOR is associated to a specific pmask. 
Therefore, when multiple AORs were available for the same galaxy, 
we merged the different pmasks. 
Cosmic ray rejection was performed with the dual outlier and multi-frame techniques.
The pixel size of the mosaic was set to be the same as the input cBCD frames ($1''.22 \times 1''.22$).
For $3.6~\rm \mu m$ observations with this pixel scale, 
the photometric zeropoint magnitude is $m_{\rm zp} = 17.26 \rm~mag$.
The orientation of the mosaic was set to the average rotation angle of the input cBCD frames. 
Individual cBCD frames were combined together into a single mosaic with the default linear interpolation algorithm.

\subsubsection{Overlap correction}
Before generating a mosaic, MOPEX can perform background matching among the individual frames
by using the \emph{overlap} module. 
This module calculates and applies an additive correction to the individual frames,
producing a consistent background across the mosaicked image.
According to the \emph{Spitzer Data Analysis 
Cookbook}\footnote{\href{http://irsa.ipac.caltech.edu/data/SPITZER/docs/dataanalysistools/cookbook/Spitzer_Data_Cookbook.pdf}
{\tt http://irsa.ipac.caltech.edu/data/SPITZER/docs/ dataanalysistools/cookbook/Spitzer\_Data\_Cookbook.pdf}}, 
the use of the \emph{overlap} module is not particularly recommended for 
$3.6~\rm \mu m$ observations. 
However, after a visual inspection of the mosaics obtained without activating the \emph{overlap} module,
we found that all the mosaics obtained from multiple AORs were affected by patchiness, 
due to bias fluctuations in the CCD array.
For this reason, we re-generated the multiple-AORs mosaics by activating the \emph{overlap} correction,
which successfully removed the ``chessboard'' pattern (see Figure \ref{fig:overlap} for an example).

@@

\subsubsection{1D PSF}
A universal, average, one-dimensional Point Spread Function was characterized using the IRAF task {\tt imexamine}.
A nonlinear least squares \citep{moffat1969} profile\footnote{The \citep{moffat1969} profile 
has the following form:
\begin{equation}
\mu = \mu_{\rm 0} - 2.5 \log \Biggl[ 1 + \biggl( \frac{R}{\alpha} \biggr)^2 \Biggr]^{-\beta} ,
\end{equation}
where $R$ is the projected radius, $\mu_{\rm 0}$ is the central surface brightness, and 
$\alpha$ and $\beta$ regulate the width and the shape of the profile.} 
of fixed center and zero background was fit to the 
(background subtracted) pixels of 20 bright stars, belonging to different image mosaics.
The best-fit parameters of the 20 stars were then averaged together. 
Doing so, we obtained 
$(\alpha, \beta) = (2''.38, 4.39)$.

\subsubsection{2D PSF}
The IRAC support team provides users with a two-dimensional instrument Point Response Function (PRF) at $3.6~\rm \mu m$.
However, while this helped remove the extended wings of saturated stars (see Section \ref{sec:aesth}), 
we found this PRF to be inadequate for the purposes of our modelling.
In fact, the $FWHM$ of the IRAC instrument PRF ($\sim 1''.8$), as measured by the IRAF task {\tt imexamine}, 
is systematically smaller than the average $FWHM$ of ``real'' stars ($\sim 2''.0$). 
Figure \ref{fig:psf} illustrates this issue.
We also tested the IRAC PRF by providing it as the input Point Spread Function (PSF) for Galfit 
and fitting a number of stars in different image mosaics.
A visual inspection of the fit residuals confirmed that the IRAC instrument PRF is narrower than ``real'' point sources.
For this reason, we constructed our 2D PSF according to the following method 
(as directed by C. Peng, private communication).\\
We provided the IRAC instrument PRF as the input PSF for Galfit 
and simultaneously fit 7 bright stars (belonging to different mosaics), 
modeling the stars with Moffat profiles 
and constraining all the profiles to have the same $(\alpha, \beta)$, position angle and axis ratio.
The 2D PSF image was then obtained by taking the best fit Moffat model -- the same best-fit model for all 7 stars, by construction -- 
and convolving it with the IRAC instrument PRF.
The advantage of this method is to obtain a 2D PSF that is wider than the instrument PRF, 
but maintains the asymmetric features of the instrument PRF (e.g.~wings and spikes).
We then tested this 2D PSF 
on a number of stars (these stars were different from the 7 stars employed to build the 2D PSF image)
and verified that it correctly reproduces the shape of ``real'' point sources.

@@

\subsection{Additional data}
\label{sec:adddata}
\subsubsection{Kinematics}
\label{sec:kinem}
A kinematical classification (slow/fast rotator) is available for 34 of our 75 galaxies 
from the ATLAS$^{\rm 3D}$ survey \citep{atlas3dIII} 
and for 3 additional galaxies from \citet{scott2014}.
This classification (Table \ref{tab:sample}, column 7) 
concerns the kinematic properties of galaxies within the spectroscopic instrument's field-of-view, 
but does not contain additional information -- crucial for our analysis -- about kinematic substructures, 
such as embedded disks or kinematically decoupled components, 
which can require separate modeling.
For this reason, we also visually inspected the velocity fields of our galaxies, 
when available from the literature.
Velocity maps were taken from the ATLAS$^{\rm 3D}$ survey for 34 galaxies 
(observed with SAURON by \citealt{krajnovic2011}),
from \citet{scott2014} for 2 galaxies 
(observed with WiFeS)
and from the SLUGGS survey for 12 galaxies 
(observed with DEIMOS by \citealt{arnold2014}).
While the field-of-views of SAURON ($33'' \times 41''$) and WiFeS ($25'' \times 38''$) 
reach to about one galaxy effective radius (for our local galaxies),
observations taken with DEIMOS can probe the galaxy kinematics well beyond two effective radii.

@@

\section{Analysis}
\label{sec:anal}
\subsection{Isophotal analysis}
We performed an isophotal analysis of our galaxies using the IRAF task {\tt ellipse} \citep{taskellipse}, 
which fits elliptical isophotes to galaxy images.
The center of the isophotes was held fixed, while the ellipticity ($\epsilon$), the position angle ($P.A.$),  
and the amplitude of the fourth harmonic\footnote{The amplitude of the fourth harmonic deviations from perfect ellipses 
($B4$) parameterizes the diskyness ($B4>0$) or boxyness ($B4<0$) of the isophotes.} ($B4$) were allowed to vary with radius.
The step in semi-major axis length between successive ellipses was first set to increase linearly, 
and then geometrically in our second run\footnote{In the case of linear steps, 
the semi-major axis length for the next ellipse was calculated by adding $1$ pixel to the current length.
In the case of geometric steps, the semi-major axis length for the next ellipse 
was calculated as $1.1$ times the current length.}.
As a result, for each galaxy we produced respectively a ``linearly sampled'' and a ``logarithmically sampled'' 
surface brightness profile along the major-axis. 
Major-axis surface brightness profiles were additionally converted into the equivalent-axis,
i.e.~the geometric mean of the major ($a$) and minor ($b$) axis ($R_{\rm eq} = \sqrt{ab}$), 
equivalent to the circularized radius.
This resulted in 4 profiles per galaxy.
Isophotes corresponding to an intensity less than 
three times the root mean square of the sky background fluctuations ($3 \times RMS_{\rm sky}$) were ignored.
Some surface brightness profiles were truncated at our discretion before the $3 \times RMS_{\rm sky}$ limit, 
according to specific technical reasons (e.g.~contamination from light of a neighboring galaxy, 
disturbed morphology in the galaxy outskirts, etc.). 
{\bf In particular, we did not attempt to fit down- or up-bendings of large-scale disks 
(e.g.~\citealt{erwin2005,erwin2008,erwin2012,gutierrez2011,comeron2012,munozmateos2013,kim2014}) 
by truncating the surface brightness profiles well before the occurrence of these features. }
Individual cases are discussed in Section \ref{sec:indgal}.

@@

\subsection{1D fitting routine}
The decomposition of the surface brightness profiles was performed with software written by G. Savorgnan.
This software can fit an observed surface brightness profile with any linear combination of 
a set of analytical functions (S\'ersic, exponential, Gaussian, Moffat, Ferrer, symmetric Gaussian ring etc. 
see Appendix \ref{sec:app1} for a description of the analytical form of these profiles).
At each iteration, 
the model is numerically convolved with a Moffat filter, to account for PSF effects, 
and then matched to the data.
The minimization routine is based on the Levenberg-Marquardt algorithm.
During the fit, we deliberately did not make use of any weighting scheme on the data points that constitute the 
surface brightness profile, 
although the use of a linearly and logarithmically sampled profile effectively represents a different weighting scheme.
The all too often over-looked flaw with (signal-to-noise)-based weighting schemes 
is that they immediately become biased weighting schemes when additional components are present but not modelled.
For example, fitting only a S\'ersic model to what is actually a nucleated elliptical galaxy immediately voids 
a (signal-to-noise)-based weighting scheme 
and results in S\'ersic parameters which describe the spheroid less accurately than had no (signal-to-noise)-weighting been used.
While we have paid careful attention to the components in each galaxy, 
this is an issue that warrants the non application of (signal-to-noise)-based weighting schemes.
{\bf Over-looked partially depleted cores, or an incorrect PSF, can of course also result in (signal-to-noise)-weighted fitting schemes 
performing poorly because of the emphasis they place on matching the model to the inner data. }

@@

that fades toward larger radii. 
{\bf Savorgnan \& Graham (\emph{submitted}) extensively discuss the topic of galaxies with intermediate-scale disks 
and show that, when these disks are misclassified and modeled as large-scale disks, 
the luminosity of the spheroidal component is underestimated, 
which makes these galaxies falsely appear as extreme outliers in the (black hole mass)-(spheroid stellar mass) diagram. } \\

@@

{\bf As noted, we were able to successfully fit bars with a Ferrer function 
(NGC 4151 is the only case for which we described the bar with a $n \sim 0.2$ S\'ersic model). 
Disk-like components embedded in the bulges of spiral galaxies were described with a $n \lesssim 1$ S\'ersic model or, 
in a few cases, with a Ferrer function\footnote{\bf The advantage of choosing a Ferrer function over a S\'ersic profile 
to fit a disk-like component embedded in the bulge 
is to reduce degeneracies with the S\'ersic profile that describes the bulge.}. 
This approach is similar to that of \cite{laurikainen2010}, 
who fit bars with a Ferrer function and inner disks with a S\'ersic model. 
We did not find evidence of bars with exponential profiles (e.g.~\citealt{elmegreenelmegreen1985,gadotti2008,kim2015}), 
but this might be due to the low number statistics of barred galaxies in our sample. }\\

@@

whereas resolved nuclear components were modeled with (PSF-convolved) narrow Gaussian functions 
{\bf (\citealt{wadadekar1999,ravindranath2001,peng2002} and \citealt{gadotti2008} discuss the importance of fitting nuclear components)}. \\

@@

@@

@@

\subsection{2D fits}
\label{sec:2d}
Two-dimensional decompositions were carried out using the software \textsc{Imfit} \citep{imfit}.
For each galaxy, we built a 2D model that was consistent with the corresponding 1D model in terms of number and type of components. 
{\bf The only difference between our 1D and 2D models pertains to the description of bars: 
because the Ferrer profile is not made available in \textsc{Imfit},
bars were fit with a 2D Gaussian function. } \\
The 2D decomposition of NGC 2974 is presented in Figure \ref{fig:n29742d}. 
The galaxy was modeled with a S\'ersic bulge, an exponential disk and a Gaussian bar.
The nuclear component was masked and the ring was not 
modeled\footnote{We built the 2D model first including and then omitting a gaussian ring component, 
but both models converged to the same solution, i.e.~the fit ``ignored'' the presence of the faint ring. 
This did not happen in the 1D decomposition because of the different weighting scheme used by the fitting routines.}. 
Our best-fit 2D model returns a bulge major-axis effective radius $R_{\rm e,sph}^{\rm maj} = 10.5~\rm arcsec$, 
a bulge S\'ersic index $n_{\rm sph} = 1.3$ and a $3.6~\rm \mu m$ bulge apparent magnitude $m_{\rm sph} = 8.39~\rm mag$, 
in fairly good agreement with our 1D decomposition. 
Fits and descriptions for the other galaxies are available online.

\begin{figure}[h]
\begin{center}
\includegraphics[width=\columnwidth]{images/n2974_imgmsk.jpeg}
\includegraphics[width=\columnwidth]{images/n2974_unsharp.jpeg}
\includegraphics[width=\columnwidth]{images/n2974_model.jpeg}
\includegraphics[width=\columnwidth]{images/n2974_resid.jpeg}
\caption{Image of the galaxy NGC 2974 with its mask (top panel, {\bf on a logarithmic scale}), 
unsharp mask (second panel, {\bf on a linear scale}), 
best-fit 2D model (third panel, {\bf on a logarithmic scale}), 
and residual image after the subtraction of the 2D model (bottom panel, {\bf on a linear scale; 
the residual patterns correspond to differences between the data and the model of less than 6\%}).
The lefthand side of the mosaic allowed an accurate determination of the sky background level.}
\label{fig:n29742d}
\end{center}
\end{figure}
